Use and acquisition of causal knowledge in a decision making process

### 2018-11-25 Propuesta/Presentacion/Presentacion_Corta.tex
añadiendo objetivos específicos

\section{Introduction}
\subsection{General Overview}
\begin{frame}
\frametitle{General Idea}
\begin{itemize}
\item We live in a causally structured world. 
\item Our actions \textit{cause} changes in the environment.
\item We consider this changes in order to plan our actions
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{A brief on causal models}
\begin{itemize}
\item Causal models encode cause-effect relations. 
\item Relations are encoded in a graph.
\item Can be used to predict \textit{effects} of certain causes
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Causal Model: Example}
\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/presentacion/example.png}
\caption{Causal graphical model for the test scenario: the target variable \textit{Lives} is causally influenced by the disease the patient has, the treatment assigned and the survival to the secondary effects of treatment.}
\label{causal_model}
\end{center}
\vskip -0.2in
\end{figure}
\end{frame}

@@

\section{Concepts}
\subsection{Causal Models}
\begin{frame}
\frametitle{Concepts}
Concepts and Framework
\end{frame}
		\begin{frame}
		\frametitle{Difference between causal and associative relations}
		\begin{itemize}
		\item With associative relations we can't figure out what influenced (or caused) what.
		\item Consider this: A distribution $p(a,t)$ can be factored both as $p(a|t)p(t)$ and $p(t|a)p(a)$. 
		\item In terms of a Bayesian Network, $T \to A$, and $A \to T$, but both can't be causal.
		\item Causal relations need not be in temporal order: consider a barometer and a storm.
		\end{itemize}
		\end{frame}

@@

\subsection{Decision Problems}
	\begin{frame}
	\frametitle{Decision Problems}
	A decision problem is composed by (\cite{bernardo2000bayesian}):
	\begin{itemize}
	\item A (rational) decision maker.
	\item A set of available options $\mathcal{A}$.
	\item A preference relation $\succeq$ defined over $\mathcal{A} \times \mathcal{A}$.
	\item A set of uncertain events $\mathcal{E}$.
    \item A set of possible outcomes $\mathcal{C}$
	\end{itemize}
	\end{frame}

@@

	\begin{frame}
	\frametitle{Justification: Explaining why}
	\begin{itemize}
	\item On the other hand, learning a causal model of an environment and using it to act upon the environment allows to \textit{explain} aspects of the model that a purely associative model would not be abel to explain. 
	\item It allows to ask \textit{why}.
	\end{itemize}
	\end{frame}

@@

\subsection{Approaches and Related Work: Causal learning in humans}
\begin{frame}
\frametitle{Causal Learning in Human beings}
\begin{itemize}
\item Human beings, while facing a sequential decision problem, use and modify causal information.
\item \cite{hagmayer2009decision}, \cite{hagmayer2013repeated} show that human beings can learn causal information in simple decision-making tasks, but remains open to study causal learning while seeking for a specific objective. 
\item 
\end{itemize}
\end{frame}
\subsection{Approaches and Related Work: Joyce's Causal Decision Theory}
\begin{frame}
\frametitle{Joyce's Causal Decision Theory}
\begin{itemize}
\item An attempt to formalize Decision Theory in the presence of Causal Information was attempted by Joyce, who stated that a decision maker must choose whatever action is more likely to (causally) produce desired outcomes.
\item  His formulation falls short since he does not consider any kind of formal causal model beyond what is commonly understood by causality
\end{itemize}
\end{frame}
\subsection{Approaches and Related Work: Bandits}
\begin{frame}
\frametitle{Bandits: Non-causal}
\begin{itemize}
\item In the class of decision problems considered for this proposal it is assumed that the a rational agent must choose some available action and then receive a reward from it.
\item Problems of this nature have been modelled as \textit{bandit} problems.
\item Best-arm algorithms exist: none consider causal information.
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Bandits: Causal bandits}
\begin{itemize}
\item An action could be conceived as an \textit{intervention} over some environment, which is in fact how humans consider actions in the world
\item They use and modify causal knowledge during a sequential decision making process.
\item It is shown by \cite{lattimoreNIPS2016} that adding causal information in a fixed budget decision problem allows the decision maker to learn \textit{faster} had he not considered causal information.
\item Their work requires that the causal model is fully known to the decision maker.
\item this requirement is relaxed later by \cite{sen2017identifying} who requires only that some part of the causal model is known and allow interventions over the unknown part. 
\end{itemize}
\end{frame}

@@

>>>>

\section{Introduction}
\subsection{General Overview}
\begin{frame}
\frametitle{General Idea}
\begin{itemize}
\item We live in a causally structured world. 
\item Our actions \textit{cause} changes in the environment.
\item We consider this changes in order to plan our actions when facing similar situations.
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{A brief on causal models}
\begin{itemize}
\item Causal models encode cause-effect relations. 
\item Relations are encoded in a graph.
\item Can be used to predict \textit{effects} of certain causes.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Causal Model: Example}
\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\includegraphics[width=\linewidth]{/Users/MauricioGS1/INAOE/Propuesta/presentacion/example.png}
\end{center}
\vskip -0.2in
\end{figure}
\end{frame}

@@

\section{Concepts}
\begin{frame}
\frametitle{Concepts}
Concepts and Framework:
\begin{enumerate}
\item Causal Models
\item Decision Problems
\end{enumerate}
\end{frame}

\subsection{Causal Models}
		\begin{frame}
		\frametitle{Difference between causal and associative relations}
		\begin{itemize}
		\item With associative relations we can't figure out what influenced (or caused) what.
		\item Consider this: A distribution $p(a,t)$ can be factored both as $p(a|t)p(t)$ and $p(t|a)p(a)$. 
		\item In terms of a Bayesian Network, $T \to A$, and $A \to T$, but both can't be causal.
		\item Causal relations need not be in temporal order: consider a barometer and a storm.
		\end{itemize}
		\end{frame}

@@

\subsection{Decision Problems}
	\begin{frame}
	\frametitle{Decision Problems}
	A decision problem is composed by (\cite{bernardo2000bayesian}):
	\begin{itemize}
	\item A set of available options $\mathcal{A}$.
	\item A (rational) decision maker with preference relation $\succeq$ defined over $\mathcal{A} \times \mathcal{A}$.
	\item A family of uncertain events $\mathcal{E}$.
    \item A family of possible outcomes $\mathcal{C}$
	\end{itemize}
	\end{frame}

@@

	\begin{frame}
	\frametitle{Justification: Explaining why}
	\begin{itemize}
	\item On the other hand, learning a causal model of an environment and using it to act upon the environment allows to \textit{explain} aspects of the model that a purely associative model would not be abel to explain. 
	\item It allows to ask \textit{why}.
	\item Transferability
	\end{itemize}
	\end{frame}

@@

\subsection{Approaches and Related Work: Causal learning in humans}
\begin{frame}
\frametitle{Causal Learning in Human beings}
\begin{itemize}
\item Human beings, while facing a sequential decision problem, use and modify causal information.
\item \cite{hagmayer2009decision}, \cite{hagmayer2013repeated} show that human beings can learn causal information in simple decision-making tasks, but remains open to study causal learning while seeking for a specific objective. 
\item 
\end{itemize}
\end{frame}
\subsection{Approaches and Related Work: Joyce's Causal Decision Theory}
\begin{frame}
\frametitle{Joyce's Causal Decision Theory}
\begin{itemize}
\item An attempt to formalize Decision Theory in the presence of Causal Information was attempted by Joyce, who stated that a decision maker must choose whatever action is more likely to (causally) produce desired outcomes.
\item  His formulation falls short since he does not consider any kind of formal causal model beyond what is commonly understood by causality
\end{itemize}
\end{frame}
\subsection{Approaches and Related Work: Bandits}
\begin{frame}
\frametitle{Bandits: Non-causal}
\begin{itemize}
\item In the class of decision problems considered for this proposal it is assumed that the a rational agent must choose some available action and then receive a reward from it.
\item Problems of this nature have been modelled as \textit{bandit} problems.
\item Best-arm algorithms exist: none consider causal information.
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Bandits: Causal bandits}
\begin{itemize}
\item An action can be conceived as an \textit{intervention} over an environment, which is in fact how humans consider their actions in the world.
\item They use and modify causal knowledge during a sequential decision making process.
\item It is shown by \cite{lattimoreNIPS2016} that adding causal information in a fixed budget decision problem allows the decision maker to learn \textit{faster} had he not considered causal information.
\item Their work requires that the causal model is fully known to the decision maker.
\item this requirement is relaxed later by \cite{sen2017identifying} who requires only that some part of the causal model is known and allow interventions over the unknown part. 
\end{itemize}
\end{frame}

@@

	\subsection{Specific Objectives}
	\begin{frame}
	\frametitle{Specific Objectives}
	In order to reach the General Objective we must:
	\begin{enumerate}

	\end{enumerate}
	\end{frame}
